Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
Update paper.qmd

Nonresponse bias occurs when participants are unwilling or unable to
answer certain questions or complete the survey. Given that our survey
takes approximately 15 minutes to complete, there is a risk of
nonresponse bias. To mitigate this,as highlighted by @surveymonkey, we
set clear expectations about the survey's purpose and estimated
completion time, encouraging participants to stay engaged. Additionally,
we apply post-stratification, adjusting survey weights to ensure that
our respondent group aligns closely with the actual population
characteristics, reducing bias and improving representativeness
[@surveylab].

@@

### Defination of the response bias

>>>>

Nonresponse bias occurs when participants are unwilling or unable to
answer certain questions or complete the survey. Handling non-response bias matters because it can skew survey results, leading to inaccurate conclusions that do not accurately represent the entire population's views or characteristics. Given that our survey
takes approximately 15 minutes to complete, there is a risk of
nonresponse bias. To mitigate this, as highlighted by @surveymonkey, we
set clear expectations about the survey's purpose and estimated
completion time, encouraging participants to stay engaged. Additionally,
we apply post-stratification, adjusting survey weights to ensure that
our respondent group aligns closely with the actual population
characteristics, reducing bias, and improving representativeness
[@surveylab].

@@

### Definition of the response bias
